Designing Types for R, Empirically

### 2020-05-16 paper/main.tex
Fix ordering

There are \PercUnitypedPositions monomorphic parameter and return value
positions in function signatures. Only \PercManytypedPositions positions have
four or more types ascribed to them. Parameter PARAMNAME of function
XXXXCOLONCOLONXXX has the maximum, XXX, types ascribed to it. Most functions
admit or return a uni-typed value.

Figure 1 provides a breakdown of the different type categories observed at
uni-typed positions.

\input{tables/uni-typed-breakdown.tex}

We observe that XXX of the positions have a single type ascribed to them, and,
only XXX have four or more types ascribed to them.

Figure XXX shows ten most common type categories that occur by
themselves. We observe that three scalar types, double, logical, and
character are most frequent. This is followed by XXX vararg parameter
positions. Next, XX\% of the parameter types are any because arguments at
those positions were either missing or unused in at least one call to those
functions. Together, these types amount to more than 50\%. This is followed
by double vector, the unit type, null, character vector, and classes matrix
and data.frame respectively.

@@

Figure shows the distribution of functions against the number of polymorphic
positions. We observe that \PercMonomorphicFunctions
(\CountMonomorphicFunctions) functions are monomorphic. The remaining
\PercPolymorphicFunctions (\CountPolymorphicFunctions) have at least one
polymorphic parameter or return type. Polymorphic functions are spread
across many packages, \CountMonomorphicPackages out of the 412 packages from our
corpus export only monomorphic functions.

>>>>

\ref{fig:unionfreq} shows the number of types inferred at each position of a
function signature. Most functions admit or return a uni-typed value. There are
\PercUnitypedPositions uni-typed parameter and return value positions in
function signatures. Only \PercManytypedPositions positions have more than three
types ascribed to them.

\input{tables/uni-typed-breakdown.tex}
\ref{fig:singlefreq} provides a breakdown of the different type categories
observed at uni-typed positions. \scalar, \class and \vector are
the most common type categories. The shaded rows correspond to polymorphic
types. Removing those gives us XXX (XXX) monomorphic positions in a corpus of
XXX parameter and return positions.

@@

\ref{fig:funpoly} shows the distribution of functions against the number of
polymorphic positions. We observe that \PercMonomorphicFunctions
(\CountMonomorphicFunctions) functions are monomorphic. The remaining
\PercPolymorphicFunctions (\CountPolymorphicFunctions) have at least one
polymorphic parameter or return type. Polymorphic functions are spread across
many packages, \CountMonomorphicPackages out of the 412 packages from our corpus
export only monomorphic functions.
